NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-06-26 paper/sentence.tex
grammar fix

At the top left of the view, the two controls \emph{Predict} and \emph{Predict All} correspond to predicting the currently displayed sentence pairs and predict all combinations of perturbed premises and hypotheses, respectively.
%
To avoid the situation where both sentences are perturbed, we ensure only one perturbation per sentence pair (i.e., we use the original premise if the hypothesis is perturbed, or use the original hypothesis if the premise is perturbed).
%%% sentence perturbation %%%%
The previously explored original sentences are stored in the dropdown list (on the right side of the buttons) that allow the user to revisit examined examples.
Also, the user can type any sentences or modify existing text in the sentence display areas to accommodate user-defined inputs.

>>>>

At the top left of the view, the two controls \emph{Predict} and \emph{Predict All} correspond to predicting the currently displayed sentence pairs and predict all combinations of perturbed premises and hypotheses, respectively.
%
To avoid the situation where both sentences are perturbed, we ensure only one perturbation per sentence pair (i.e., we use the original premise if the hypothesis is perturbed, or use the original hypothesis if the premise is perturbed).
%%% sentence perturbation %%%%
The previously explored original sentences are stored in the dropdown list (on the right side of the buttons) that allows the user to revisit examined examples.
Also, the user can type any sentences or modify existing text in the sentence display areas to accommodate user-defined inputs.
